Stability of flower visitation rate over time is driven by asynchrony of pollinator abundances but does not determine the stability of plant reproductive success.

### 2023-03-15 Manuscript/Manuscript.Rmd
Discussion

Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021]. To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate [@Garibaldi2011; @Garibaldi2013; @Hunicken2021], although in our study system (wild plants), we did not find this relationship.
However, we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, even if there is a saturation of the proportion of fruits in most of the plant species analysed.
As the number of pollinator visits received by a plant increases from zero, the reproductive success of the plant is expected to rise initially but then to level off or possibly decline [@Young1992; @Morris2010]. Bees can remove 70–80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits. Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001]. Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.    
One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero decir que nosotros no sabemos si esos años los plots tenian mas abundancia y diversidad de flores, nosotros tenemos las flores de las especies analizadas pero no del resto). These factors can mediate pollination through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017]. The concentration effect, which occurs when foragers visit a location in greater numbers due to high resource availability [@Kunin1996; @Totland1998], has an impact on the reproductive success of plants [@Blaauw2014; @Cohen2021]. Furthermore, some plant species increase pollinator visits to the coflowering plant, which subsequently contributes to the reproductive success of neighbouring individuals [@Schemske1981; @Moeller2004; @Ghazoul2006].
Another possible explanation to this might be the variations in abiotic factors.  Since the weather conditions can vary significantly between years, the abundance of pollinators during the flowering season of a plant can show annual variations, which may have an impact on the plant reproductive success [@Vicens2000; @Ivey2003]. In addition, the environmental conditions also affect to host plants. For instance,  the variation of temperature conditions lead to alterations in nectar production, composition and concentration [@Pacini2003], which can affect to the pollinator activity.

>>>>

Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021]. To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate [@Garibaldi2011; @Garibaldi2013; @Hunicken2021], although in our study system (wild plants), we did not find this relationship.
However, we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, even if there is a saturation of the proportion of fruits in most of the plant species analysed.
As the number of pollinator visits received by a plant increases from zero, the reproductive success of the plant is expected to rise initially but then to level off or possibly decline [@Young1992; @Morris2010]. Bees can remove 70–80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits. Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001]. Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.    
One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero decir que nosotros no sabemos si esos años los plots tenian mas abundancia y diversidad de flores, recursos disponibles, nosotros tenemos las flores de las especies analizadas pero no del resto). These factors can mediate pollination through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017]. The concentration effect, which occurs when foragers visit a location in greater numbers due to high resource availability [@Kunin1996; @Totland1998], has an impact on the reproductive success of plants [@Blaauw2014; @Cohen2021]. Furthermore, some plant species increase pollinator visits to the coflowering plant, which subsequently contributes to the reproductive success of neighbouring individuals [@Schemske1981; @Moeller2004; @Ghazoul2006].
Another possible explanation to this might be the variations in abiotic factors.  Since the weather conditions can vary significantly between years, the abundance of pollinators during the flowering season of a plant can show annual variations, which may have an impact on the plant reproductive success [@Vicens2000; @Ivey2003]. In addition, the environmental conditions also affect to host plants. For instance,  the variation of temperature conditions lead to alterations in nectar production, composition and concentration [@Pacini2003], which can affect to the pollinator activity.
Although we have not taken these factors into account in our study, we believe it is important to include them in order to better understand the relationships between pollinators and plant reproductive success over time.

In summary, our study highlights the importance of pollinator species' asynchrony in maintaining the temporal stability of these communities in natural environments. However, this stability did not contribute to the stability of the function. In this sense, we believe that further studies are needed to better understand these mechanisms in natural communities by assessing the reproductive success of a wider variety of plant species. 
The variations seen between years suggest that in our study system, plant reproduction is not typically limited by pollinators. However in certain years the relationship between pollinator activity and plant reproductive success is important. This study contributes to understanding the mechanisms driving the temporal stability of pollinator communities in natural systems and how the relationships between pollinators and plant reproductive success may vary from year to year.
